---
title: "Week9"
output: html_document


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Home work requirement: The New York Times web site provides a rich set of APIs, as described here http://developer.nytimes.com/docs . The goal of the Week 9 assignment is to use one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.

## Time: "Oct 25 2018"



#load libraries
```{r}
 library(httr)
 library(jsonlite)
library(knitr)
library(kableExtra)
library(tidyverse)
```

# provide API information and Get content 
```{r}
#params
api.key <- "3425bcc40327445bbb77b6245a2a7efc"
 
#return JSON from NYT API
url <- "https://api.nytimes.com/svc/books/v3/lists/best-sellers/history.json";
query_list <- list( "api-key"=api.key )
request <- GET(url,query=query_list)
request

```

## Extract data 

```{r}
content <- content(request, "text")
bookseller_data <- fromJSON(content)
results <- as.data.frame(bookseller_data$results)
 
```

## choose target columns from dataframe
```{r}
colnames(results)
df <- results %>% select(c(1,3,6,7:9))
colnames(df)
 
```

#visualization of results ( # of books per publisher )
Creating an aggregated data frame from the above to find the publishers popularity. And plot them in a graph
```{r}
df %>%
   filter (!is.na(publisher))%>%
   group_by(publisher) %>%
  summarise(cnt = n()) %>%
  ggplot(aes(x = reorder(publisher,cnt), y = cnt)) +
  geom_bar(stat = "identity" , aes(fill= publisher)) +
          coord_flip()  +
         theme(
          panel.grid.minor.y = element_blank(),
         panel.grid.major.y = element_blank(),
            legend.position = "none"
          ) +
          ylab("Count")+ xlab("Publisher")




```



```{r , echo=FALSE}
 
```

