---
title: "Data607_Project3"
date: "October 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#install packages
```{r }
#install.packages("RSQLite")
#install.packages('tidyverse')
#install.packages('dplyr')
```

#load library 
```{r}
library(RSQLite)
library(tidyverse)
library(dplyr)
```

#Create SQLite DB
```{r}
# Create an ephemeral in-memory RSQLite database
con <- dbConnect(RSQLite::SQLite(), ":memory:" ,overwrite =TRUE )
dbListTables(con)
```
#load data from csv files 
```{r}
df <-  read.csv(file = "kaggle-survey-2017/multipleChoiceResponses.csv", header= TRUE)
df_freeResponse <- read.csv (file = "kaggle-survey-2017/freeformResponses.csv", header= TRUE)
df_CRate<- read.csv (file = "kaggle-survey-2017/conversionRates.csv", header= TRUE)
df_schema <- read.csv (file = "kaggle-survey-2017/schema.csv", header= TRUE)

```
#Add Sequence ID to the dataset
```{r}
# add sequence to the dataframe 
df<- tibble::rowid_to_column(df, "ID")
```
## Select columns for the project 
# columns ID refer to the "multipleChoiceResponses_columnsID.xlsx" file 

```{r}
target_col <- c ("ID",  "GenderSelect" ,"Country", "Age"  ,"EmploymentStatus"                  ,"StudentStatus"                     ,"LanguageRecommendationSelect"  ,    "JobSkillImportanceBigData"   ,"JobSkillImportanceDegree" ,         "JobSkillImportanceStats" ,"JobSkillImportanceEnterpriseTools", "JobSkillImportancePython"  ,"JobSkillImportanceR"  ,             "JobSkillImportanceSQL"     ,"JobSkillImportanceKaggleRanking" ,  "JobSkillImportanceMOOC"  ,"JobSkillImportanceVisualizations")

df_target <- df[,target_col]

```
#clean up columns
#show unique value in jobimportanceXXX columns
```{r}
table(df_target$JobSkillImportanceDegree)
df_target %>% select (starts_with("Jobs")) %>% str()

table(df_target$JobSkillImportanceBigData)
```


#clean JobskillImportanceXXX columns

```{r}

JobImportance <- function(skill)
{  skill<- as.character(skill)
     if (skill=='Necessary')
     {
       return (2)
       
     }
    else if (skill=="Nice to have")
    {
      return (1)
    }
  else if (skill=="Unnecessary")
{
    return (-1)
  
  
}
  else 
  {
    return (0)
  }
}

df_target$JobSkillImportanceBigData <- sapply(df_target$JobSkillImportanceBigData, JobImportance)
df_target$JobSkillImportanceDegree <- sapply(df_target$JobSkillImportanceDegree, JobImportance)
df_target$JobSkillImportanceStats <- sapply(df_target$JobSkillImportanceStats, JobImportance)
df_target$JobSkillImportanceEnterpriseTools <- sapply(df_target$JobSkillImportanceEnterpriseTools, JobImportance)
df_target$JobSkillImportancePython <- sapply(df_target$JobSkillImportancePython, JobImportance)
df_target$JobSkillImportanceR <- sapply(df_target$JobSkillImportanceR, JobImportance)
df_target$JobSkillImportanceSQL <- sapply(df_target$JobSkillImportanceSQL, JobImportance)
df_target$JobSkillImportanceKaggleRanking <- sapply(df_target$JobSkillImportanceKaggleRanking, JobImportance)
df_target$JobSkillImportanceMOOC <- sapply(df_target$JobSkillImportanceMOOC, JobImportance)
df_target$JobSkillImportanceVisualizations <- sapply(df_target$JobSkillImportanceVisualizations, JobImportance)


```

#show the result after clean up 
```{r}
df_target %>% select (starts_with("Jobs")) %>% str()
```

#clean GenderSelect columns

```{r}
table(df_target$GenderSelect )


GenderClean <- function(gender)
{  skill<- as.character(gender)
     if (gender=='Female')
     {
       return ('F')
       
     }
    else if (gender=="Male")
    {
      return ("M")
    }
  
  else 
  {
    
    return ("NA")
  }
  
}
df_target$GenderSelect <- sapply(df_target$GenderSelect, GenderClean)
df_target$GenderSelect <- sapply(df_target$GenderSelect, factor)
table(df_target$GenderSelect )
```

```{r}
str(df_target)
```


#clean up EmploymentStatus
```{r}
table (df_target$EmploymentStatus )

EmployeeClean <- function(emp)
{  emp<- as.character(emp)
     if (emp=='Independent contractor, freelancer, or self-employed')
     {
       return ('Self-employed')
       
     }
    else if (emp=="Not employed, and not looking for work"|emp=="Not employed, but looking for work")
    {
      return ("Unemployed")
    }
  else if (emp=="I prefer not to say")
    {
      return ("NA")
  }
else if (emp=="Employed full-time")
    {
      return ("Full_Time")
}
else if (emp=="Employed part-time")
    {
      return ("Part_Time")
    }
  else 
  {
    
    return (emp)
  }
  
}
df_target$EmploymentStatus <- sapply(df_target$EmploymentStatus, EmployeeClean)
df_target$EmploymentStatus <- sapply(df_target$EmploymentStatus, factor)
table(df_target$EmploymentStatus )
```



```{r}
str(df_target)
```


#visulationzation

```{r}
df_jobimportance <-  df_target %>% 
  select (starts_with("Jobs")) 
names(df_jobimportance) <- sub ("JobSkillImportance" , "", names(df_jobimportance))
#colSums()
par(las=2) # make label text perpendicular to axis
par(mar=c(5,8,4,2)) # increase y-axis margin.
barplot(colSums(df_jobimportance), horiz=TRUE)
```





```{r}
dbWriteTable(con,  "MCR_Target_Analysis_Tab", df_target)
dbWriteTable(con,  "MCR_FreeResponse", df_freeResponse)
dbWriteTable(con,  "MCR_Schema", df_schema)
dbWriteTable(con,  "MCR_CurrencyRate", df_CRate)
dbWriteTable(con,  "MCR_multipleChoiceResponses", df )
dbListTables(con)

```
#Show available columns 

```{r}
dbListFields(con, "MCR_Target_Analysis_Tab")
```

#close DB conncetion

```{r}
 dbDisconnect(con)
```

