---
title: "Data607_Project3"
date: "October 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#install packages
```{r }
#install.packages("RSQLite")
#install.packages('tidyverse')
#install.packages('dplyr')
```

#load library 
```{r}
library(RSQLite)
library(tidyverse)
library(dplyr)
```

#Create SQLite DB
```{r}
# Create an ephemeral in-memory RSQLite database
con <- dbConnect(RSQLite::SQLite(), "ML_Survey.sqlite" ,overwrite =TRUE )
dbListTables(con)
```
#load data from csv files 
```{r}
df <-  read.csv(file = "H:/Learning/MS_DataScience/607_DataAcquisition_And_Management/Project3/kaggle-survey-2017/multipleChoiceResponses.csv", header= TRUE)

```
#Add Sequence ID to the dataset
```{r}

# add sequence to the dataframe 
df<- tibble::rowid_to_column(df, "ID")
```
## Select columns for the project 
#do we need to add columns  135:164 and 83:130??
# columns ID refer to the "multipleChoiceResponses_columnsID.xlsx" file 
```{r}
col_index <- c(1:15, 38:47,70:82,134,168:172,208:211)
df2 <- df[,col_index]
```


#load data into SQLlite

```{r}
dbWriteTable(con,  "MCR_Tb", df2)
dbListTables(con)

```
#Show available columns 

```{r}
dbListFields(con, "MCR_Tb")
```

#close DB conncetion

```{r}
 dbDisconnect(con)
```

# Next steps : 
# Confirm the list of columns 
# Clean multiple choice data 
# Convert category data 
# Select sub_dataset for example US Full_employeed 
# Deal with missing data 
# Objects : Determine which factors affecting the salary of US employee in Data Science field. 
# Build ML model



```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
