

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(readr)
```
 :

```{r }
fileName<-"tournamentinfo.txt"
sourcefile <- read_lines(fileName)
```

#show sample source file 

```{r}
sourcefile[1:14]
```

 

```{r}
#load data into one dataframe and separate data by lines
df =  data.frame(c())
newfilelist = NULL
newfilelist2= NULL
df = NULL
for (i in seq(5, length(sourcefile), by=3))
  
{
  newfilelist <- append(newfilelist, sourcefile[i])
  newfilelist2 <- append(newfilelist2, sourcefile[i+1])
  newRow <-  data.frame(paste0(newfilelist, newfilelist2))
#  print (newRow)

  
}

df <- rbind(df, newRow)
```


```{r}
 
colnames(df ) <- c('all_col')
head(df)
```

#Separe the comumn into multiple columns 
```{r}
 headers  <- c("Pair","Player Name","Total","Round 1","Round 2","Round 3", "Round 4","Round 5","Round 6","Round 7","State","USCF","Pts","1","2","3","4","5","6","7","Ave_Rating")

 
```

#load tidyr package and separate cols with "|"

```{r}
library(tidyr)
library(dplyr)
target_df <- separate(data = df,col = all_col ,into = headers ,sep='\\|' )
head(target_df)
```



```{r}
target_df <- target_df%>% separate( 'USCF', into = paste("V", 1:5), sep = '[[:punct:]->]')  

```



```{r}
 #delete column v2, v4
target_df <- select (target_df, -c('V 2','V 4'))
#rename v1 --> USCF ID  v3 -->Pre Rating v5-->Post Rating
target_df <- target_df %>% rename('USCF_ID'= 'V 1') %>% rename('Pre_Rating'= 'V 3') %>%rename('Post_Rating'= 'V 5')
head(target_df)
```
#Calculating Average Pre Rating
 


```{r}
df_score<-target_df 
df_score$opp1<-  as.numeric(str_extract (df_score$`Round 1`,"[[:digit:]]{1,}"))
df_score$opp2<-  as.numeric(str_extract (df_score$`Round 2`,"[[:digit:]]{1,}"))

df_score$opp3 <-  as.numeric(str_extract (df_score$`Round 3`,"[[:digit:]]{1,}"))
df_score$opp4  <-  as.numeric(str_extract (df_score$`Round 4`,"[[:digit:]]{1,}"))
df_score$opp5  <-  as.numeric(str_extract (df_score$`Round 5`,"[[:digit:]]{1,}"))
df_score$opp6  <-  as.numeric(str_extract (df_score$`Round 6`,"[[:digit:]]{1,}"))
df_score$opp7  <-  as.numeric(str_extract (df_score$`Round 7`,"[[:digit:]]{1,}"))
```




```{r}
head(df_score)
```

#prepare opponets dataframe
```{r}
#get opponents dataframe 
opponents <- select(df_score, Pair,'Player Name',Total, starts_with("opp"))
#cal total N of games per player
opponents$total_N_Games <- apply(opponents, 1, function(x) 7-sum(is.na(x)))  
opponents$Pair <- as.numeric(str_extract (df_score$Pair ,"[[:digit:]]{1,}")) 
#fill in NA with 0
opponents[is.na(opponents)] <- 0

  
```

#prepare player dataframe 

```{r}
player <- select (target_df, Pair,'Player Name',State, 'USCF_ID', Total, 'Pre_Rating', 'Post_Rating' , 'Ave_Rating')
#pase numberic value from both Pre_Rating and Post_Rating 
player$Pre_Rating<-  as.numeric(str_extract (player$Pre_Rating,"[[:digit:]]{1,}"))
player$Post_Rating<-  as.numeric(str_extract (player$Post_Rating,"[[:digit:]]{1,}"))
player$Pair <-  as.numeric(str_extract(player$Pair,"[[:digit:]]{1,}"))
player$Ave_Rating <- 0
```



#  calculate Average Pre-Rating for each player
```{r}

for (k in 4:10)
  {
  for (j in 1:dim(player)[1])
    {
    for (i in 1:dim(player)[1]){
    
      if (as.numeric(opponents[j,k]) == as.numeric(player$Pair[i])){
          # print (player$Pair[i])
         player$Ave_Rating[j] <- as.numeric(player$Ave_Rating[j]) + as.numeric(player$Pre_Rating[i])
        # print (player$Ave_Rating[j])
      }
    }
  }

}
```


```{r}
head(opponents)
```



```{r}
head(player)
```


#merge two dataframes and calculate total Average rating 

```{r}
df_summary <- merge(x= player, y = opponents, by ='Pair' , all.x = TRUE)
df_summary <- select(df_summary, -c('Total.y' ,'Player Name.y') )
df_summary$Ave_Rating <- df_summary$Ave_Rating/df_summary$total_N_Games 

head(df_summary)
```

#show distribution of players by state

```{r}
library(ggplot2)


```

```{r}
pl <- ggplot(df_summary, aes(x=State))
print(pl+geom_bar(aes(fill=State)))
```



#load final data into csv file 


```{r}
write.table(df_summary, file = "tournamentInfo.csv",row.names=FALSE, na="",col.names=TRUE, sep=",")
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
