---
title: "Week2_Assignment"
output: html_document
---


## R Markdown

#load movie dataset(csv files ) to R 
```{r}
movie= read.csv('movies.csv', header = TRUE)
head(movie,5)
```



```{r}
ratings= read.csv('ratings.csv', header = TRUE)
ratings$ratingtime = as.POSIXct(ratings$timestamp, origin="1970-01-01", tz="UTC")

```


```{r}
head(ratings)
```


 # load RMySQL package
```{r}
library(RMySQL)
```


# Load Login info from configuration file 
```{r}
rmysqlsql.settingfile <- 'H:\\Learning\\MySQL_Configuration_file.cnf'
rmysql.db ="Movies"
```

# Build connection to local MySQL server ( Version 5.7)

```{r}
conn <- dbConnect(MySQL(),  default.file= rmysqlsql.settingfile, group = rmysql.db)

```

#check avialble tables (new schema no tables avialble in the schema)
```{r}
dbListTables(conn)
```


## load movies into movies schema 
```{r}
dbWriteTable(conn, value = movie, row.names = FALSE, name = "movies", append = TRUE ) 
```


#load ratings into movies schema 
```{r}
dbWriteTable(conn, value = ratings, row.names = FALSE, name = "ratings", append = TRUE ) 
```

#check the avavilable table 

```{r}
dbListTables(conn)
```

# read sample data from movies table 

```{r}
movie_query <- "SELECT * FROM movies.movies where title like ('%2016%') order by movieid desc
limit 10
; "
movie_result = dbGetQuery(conn, movie_query )
movie_result
```

#read sample data from ratings table 

```{r}
ratings_query <- "SELECT * FROM movies.ratings where rating >=4.0 order by ratingtime desc
limit 10
; "
ratings_result = dbGetQuery(conn, ratings_query )
ratings_result
```


#Get the average rating of the movies in 2016

```{r}
movie_Avg_rating_qry =  "SELECT r.movieid, title, AVG(COALESCE(r.rating,0)) AS Averge_rating
FROM movies.ratings r 
INNER JOIN movies.movies m ON r.movieid = m.movieid 
WHERE m.title LIKE'%2016%' 
GROUP BY r.movieid, title
"
movie_Avg_rating_result = dbGetQuery(conn, movie_Avg_rating_qry)

```
#list the movies with average rating >4.5
```{r}
subset(movie_Avg_rating_result,Averge_rating>=4.5)
```


