---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




#import package
```{r}
library(stringr)

```


#Load data
```{r cars}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
```

#Extract phones and names 

```{r}
phone <- "[(]*[0-9]{3}[- .)]*[0-9]*[- .]*[0-9]{4}"
phone_number <- str_extract_all(raw.data, phone, simplify = TRUE)
phone_number

```


```{r}
names = unlist(str_extract_all(raw.data, "[[:alpha:].,  ]{2,}"))
print(names)
print(paste0 ("Vector: ", is.vector(names)))
```




#extract last name , first name and title 

```{r}

fullName.list <-str_extract_all(raw.data, "[[:alpha:].,  ]{2,}", simplify = TRUE)
fullName.list
  
  #"^[[:alpha:]]{2,}+\\[.]"
#print (str_extract_all(names, title.pattern, simplify = TRUE))
 
```


```{r}
#creat empty Datafram 
df <- data.frame(Title =character(),
                 First_Name=character(),
                 Last_Name=character(), 
                 stringsAsFactors=FALSE) 
```


#extract title , FristName , LastName
```{r}
#remove titles first 
j=1
for (i in fullName.list)
{
   
  title = str_extract(i, "^[[:alpha:]]{2,}[.]")
  name2  =str_replace_all(i, "^[[:alpha:]]{2,}[.]", '') 
  
   if (grepl(",", name2)){
     name3 <- str_split(name2, ",", simplify = TRUE)
     newRow <- data.frame(Title =title, First_Name = name3[2],Last_Name=name3[1] )
     df <- rbind(df, newRow)
   
     #print (name3)
   }
  else{
    name3 = str_extract_all(name2, "[[:alpha:]]+[^[.]]", simplify = TRUE) 
    newRow <- data.frame(Title =title, First_Name = name3[1], Last_Name=name3[2])
    df <- rbind(df, newRow)
  }
  
  j <- j+1
}

```


#3-1 oragniaze all elments to standard first_name, lastname  
```{r}

df[,2:3]
 
```

#3-2 Construct a logical vector indicating whether a character has a title


```{r}
vector.withTitle <- str_detect(names, "^[[:alpha:]]{2,}[.]")
vector.withTitle
```

# checck from dataframe

```{r}
df$No_title <- is.na(df$Title)
df
```


#Contruct a logical vector that indicates if a character has a second name
```{r}
secondname <- str_detect(names," [A-z]{1}\\. ")
secondname
```

```{r}
df$No_title <- is.na(df$Title)
df$SecondName <- grepl("[.]", df$First_Name)
df
```
 

#4.Describe the Types of Strings that conform to the following regular expressions and contruct an example that is matched by the regular expression
# [0-9]+\\$


```{r}
# any character end with number+$ 
p1 <-   "[0-9]+\\$"
sampletext <- c("5555", "ssdf33$" ,"334a" ,"333$")
str_detect( sampletext, p1)



```

#\\b[a-z]{1,4}\\b
```{r}
# #Any word that has anywhere between 1 to 4 letters end with word boundary
p1 <-   "\\b[a-z]{1,4}\\b"
sampletext <- c(" New york city", "cats dogs" ,"cats" ,"333$")
str_detect( sampletext, p1)

```

# .*?\\.txt$
```{r}
# A string that ends with a .txt and then new line or end line
p1 <-   ".*?\\.txt$"
sampletext <- c(" New york city.txt", "newbook.txt" ,"movie.txt" ,"movie.xlx")
str_detect( sampletext, p1)

```
 


#\\d{2}/\\d{2}/\\d{4}

```{r}
# #Numbers that are written in format nn/nn/nnnn
p1 <- "\\d{2}/\\d{2}/\\d{4}"
sampletext <- c("20/12/2018", "05-05-2016" ,"06/12/2012" )
str_detect( sampletext, p1)

```
#<(.+?)>.+?</\\1>
```{r}
# chose string from html format  <target> text </+target) 
p1 <- "(.+?)>.+?</\\1>"
sampletext <- c("<test>hello</test>", "<text>hello<text>")
str_detect( sampletext, p1)

```

#9. Extra Credit-The following code hides a secret message. Crack it with R and regular expressions.



```{r}
secret_code <-"clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
```

#extract upper case letter
```{r}
uppercaseletters <- str_extract_all(secret_code, "[[:upper:].]{1,}",simplify = TRUE)
uppercaseletters 


```

#join list and replece ". " with " "

```{r}
str_replace_all(paste(uppercaseletters, collapse = ''), "[.]", " ")
```


 
