---
title: "Week5Assignments"
 
date: "September 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
library(dplyr)
library(tidyr)
```

##  Load Data
```{r}

flights<-  read.csv("flight.csv", stringsAsFactors = FALSE, check.names = FALSE)
flights
```
```{r}
head(flights,2)
```


# Add column names
```{r}
col <- c('Airline','Status','Los Angeles','Phoenix','San Diego', 'San Francisco', 'Seattle')
colnames(flights)<-col

```


#drop na rows

```{r}
row.toberemoved <- which (flights$Status=="")
df <- flights[-row.toberemoved,]
df
```

#fill in the missing value
```{r}
df[2,1]='ALASKA'
df[4,1]='AM WEST'
df
```

 #clean up with tidyr
```{r}
df2 <- df %>% 
  gather(City, freq, 3:length(flights)) %>%   # Transfer 'city' variable into a column
  spread(Status, freq)%>% rename ( on.time ='on time')

df2
```


#df

```{r}
df2
```


#Data Analysis
# getting the ratio of delayed flights for all airlines and cities.

```{r}
df2 <- df2 %>% 
  mutate(Total_flights = delayed +on.time, delayed_ratio = delayed / Total_flights) %>% 
  arrange(desc(delayed_ratio))

df2
```

#plot the relationship between total flights and delayed ratio
#load library
```{r}
library(ggplot2)

```

#load library

```{r}
p1 <- ggplot(df2, aes(x= Total_flights, y= delayed_ratio, colour='red'))
print (p1+geom_point())
```
It seems that there is no liner relation ship between total number of fights and the ratio of air line delay events. 

 